Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-25 sattose/paper.tex
Writing about type 2 clones

>>>>

In this chapter, we will discuss type-2 and type-3 clones (because type-1 clones are straightforward and type-4 clones are out of the scope for this study).

\subsection{Type 2 clones}
Type 2 clones, by definition, allow any change in identifiers, literals, types, layout and comments. For refactoring purposes, this doesn't always make a lot of sense. If we allow any change in identifiers, literals and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones. Merging such clones, if possible at all, might only proof to be harmful.

Because of that, for this research we have looked into a redefinition of type 2 clones to be able to detect such clones that can and should be merged. Our definition ensures functional similarity by considering types, having a distinction between different variables and defining thresholds for variability in literals.

%TODO: Show the stuff

\subsection{Type 3 clones}

%TODO: Write this chapter
